Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-23 main.tex
modify-ver1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%% \usepackage{subfigure}
\usepackage{subfig}
%% \usepackage{subcaption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration strategy foer mismatch condition\\
{\footnotesize \textsuperscript{}}}

@@

\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system reduced significantly under partial shading or solar cell damage etc. conditions. Which affected of turned on bypass diode. These efficiency loss in the form of mismatch losses. Using reconfiguration technology to reconfigure electrical connection, which, changing series or parallel connetion among PV panel can minimize mismatch losses. However existed reconfiguration methods such as exhaustive search or Genetic algorithm(GA) need very long computing time to find best configuration. This paper proposed an reconfiguration strategy that find optimal configuration among mismatched PV array in a very less computational time. This algorithm is very light and suitble for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

\section{Introduction}

As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human. Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up. Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application. But due to PV arrays are senstive to shading and PV cell's fault or aging. That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another. PV arrays are in mismatch condition. In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can re-configurate photovoltaic arrays to minimize mismatch loss.

In this paper, we using non-uniform irradiance levels to represent mismatch condition and analyzes the efficiency of a PV system under different shaded working condition is presented. When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which been generated by turning on bypass diodes. By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.

The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading, so there may be more than one MPP for each panel. Reconfiguration strategy need also consider to group PV modules which provided high power separately\cite{b3} \cite{b4}.

This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels. The reconfiguration algorithm will analyzes panels' working conditions and reorganizes panels into different strings by different irradiance levels. However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant. For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.Another approach to optimize photovoltaic arrays is using genetic algorithm\cite{b5}. However, computing cost is too significant, and this algorithm can't detect best configuration precisely.

\section{Assumption of a PV array} \label{assum}
In this paper, we using following definitions of PV arrays, modules, strings and panels. A PV array formed by several parallel connected PV strings, and string is several series connected PV panels. For a PV panel, formed by two or three PV modules connected in series with bypass diodes. An equivalent connection as showed in Fig. \ref{fig1}.
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{Definition of PV array and internal components.}
\label{fig1}
\end{figure}

The algorithm we proposed based on following assumptions.
\begin{itemize}
\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}. This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
\item All the panels in PV array have same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}. Those parameter can be directly estimated by the prosess provided in\cite{b7}.
\end{itemize}

Furthermore, it is also assumed that for each string it has same number of panels in PV array. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{paper-fig2.png}}
\caption{Flowchart of reconfiguration algorithm.}
\label{fig2}
\end{figure}

\section{Reconfiguration Algorithm}
The general steps of reconfiguration algorithm are presented in Fig. \ref{fig2}. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}. Afterward, determine real number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shading distribution among PV array.  Then grouping panels into different shadow distribution.

@@

\begin{thebibliography}{00}
\bibitem{b1} Koutroulis, Eftichios, and Frede Blaabjerg. "A new technique for tracking the global maximum power point of PV arrays operating under partial-shading conditions." IEEE Journal of Photovoltaics 2.2 (2012): 184-190.
\bibitem{b2} La Manna, Damiano, et al. "Reconfigurable electrical interconnection strategies for photovoltaic arrays: A review." Renewable and Sustainable Energy Reviews 33 (2014): 412-426.
\bibitem{b3}Storey, Jonathan, Peter R. Wilson, and Darren Bagnall. "The optimized-string dynamic photovoltaic array." IEEE Transactions on Power Electronics 29.4 (2014): 1768-1776.
\bibitem{b4} Storey, Jonathan P., Peter R. Wilson, and Darren Bagnall. "Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.
\bibitem{b5} P. Carotenuto, A. D. Cioppa, A. Marcelli, and G. Spagnuolo, “An evolu- tionary approach to the dynamical reconfiguration of photovoltaic fields,” Neurocomputing, vol. 170, pp. 393–405, 2015.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
\bibitem{b8} Spagnuolo, Giovanni, et al. "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
\bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
\bibitem{b11} El-Dein, MZ Shams, Mehrdad Kazerani, and M. M. A. Salama. "Optimal photovoltaic array reconfiguration to reduce partial shading losses." IEEE Trans. Sustain. Energy 4.1 (2013): 145-153.
\bibitem{b12} Storey, Jonathan P., Peter R. Wilson, and Darren Bagnall. "Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%% \usepackage{subfigure}
\usepackage{subfig}
%% \usepackage{subcaption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
{\footnotesize \textsuperscript{}}}

@@

\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions. This efficiency losses affected by truing on bypass diode of PV panels, which called mismatch losses. Reconfiguration technology to reconfigure electrical series or parallel connection among PV panel can maximize generate power. This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time. This algorithm is very light and suitable for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

\section{Introduction} \label{intro}

As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being. Photovoltaic (PV) energy has received a significant attention since it is unlimited and easy to be scaled up. Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation systems have been deployed into many practical applications. However, PV arrays are sensitive to shading and PV cell's fault or aging. This implies that when interconnection of PV cells or modules do not have identical properties or experience different conditions from one another. the PV array is in mismatch condition. The photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array. In order to avoid mismatch condition damage PV cells, we propose an algorithm that can reconfigure photovoltaic arrays to avoid mismatch damage and maximize generated power.

In this paper, we use non-uniform irradiance levels to represent mismatch condition and analyze the efficiency of a PV system under different shaded working condition. Photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which are generated by turning on bypass diodes. By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.

The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading and there may be more than one MPP for each panel. Moreover, the panels, and not modules, reconfiguration strategy has to be realized so that modules providing the highest power could be grouped separately\cite{b3} \cite{b4}.

This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels. The reconfiguration algorithm will analyzes panels' working conditions and reorganizes panels into different strings by different irradiance levels. However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant. For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}. Another approach to optimize photovoltaic arrays is using genetic algorithm\cite{b5}. However, computing cost is too significant, and this algorithm can't detect best configuration precisely. A simplest reconfiguration strategy for minimizing mismatch losses is presented in \cite{b10}. In this strategy, an algorithm gives candidates for PV array reconfiguration, for each candidates we have conduct power simulations. But some candidates are not feasible, which means there isn't any configuration for PV array can be realized. Since the power simulation is very time consuming, based on existed work we want to reduce number of candidates to accelerate overall reconfiguration algorithm. In this paper we propose an algorithm can give optimal configuration and check feasibility with less computational time and high accuracy.

\section{Assumption of a PV array} \label{assum}
In this paper, we use the following definitions of PV arrays, modules, strings and panels as showed in Fig. \ref{fig1}. A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels. For a PV panel, formed by three PV modules connected in series with bypass diodes. 
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{PV arrays, strings, and panels.}
\label{fig1}
\end{figure}

We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}. That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not.

All the panels in PV array have the same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}. Those parameters can be directly estimated by the prosess provided in\cite{b7}.

Furthermore, it is also assumed that for each string it has same number of panels. Means every string in PV array have same length. String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{flowchart.png}}
\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
\label{flowchart}
\end{figure}

\section{Reconfiguration Algorithm} \label{algo}
As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}. Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates. Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array. Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations. The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}.

\subsection{Feasibility}
The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels. Definition of feasibility in (\ref{feas}). When a configuration needs panels in a string (\textit{$NP_n$}) are over mean value for number of panels per-string this configuration is unfeasible. 
\begin{equation}
\left\{\begin{matrix}
NP_n > NP\div N_{st}& & \text{Unfeasible}\\ 
NP_n \leq NP\div N_{st} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}

\subsection{Reconfiguration strategy}
Based on existed reconfiguration
%The general steps of reconfiguration algorithm are presented in Fig. \ref{fig2}. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}. Afterward, determine real number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shading distribution among PV array.  Then grouping panels into different shadow distribution.

@@

\begin{thebibliography}{00}
\bibitem{b1} Koutroulis, Eftichios, and Frede Blaabjerg. "A new technique for tracking the global maximum power point of PV arrays operating under partial-shading conditions." IEEE Journal of Photovoltaics 2.2 (2012): 184-190.
\bibitem{b2} La Manna, Damiano, et al. "Reconfigurable electrical interconnection strategies for photovoltaic arrays: A review." Renewable and Sustainable Energy Reviews 33 (2014): 412-426.
\bibitem{b3}Storey, Jonathan, Peter R. Wilson, and Darren Bagnall. "The optimized-string dynamic photovoltaic array." IEEE Transactions on Power Electronics 29.4 (2014): 1768-1776.
\bibitem{b4} Storey, Jonathan P., Peter R. Wilson, and Darren Bagnall. "Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.
\bibitem{b5} P. Carotenuto, A. D. Cioppa, A. Marcelli, and G. Spagnuolo, “An evolu- tionary approach to the dynamical reconfiguration of photovoltaic fields,” Neurocomputing, vol. 170, pp. 393–405, 2015.
\bibitem{b6} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
\bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
\bibitem{b8} Spagnuolo, Giovanni, et al. "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
\bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
\bibitem{b11} El-Dein, MZ Shams, Mehrdad Kazerani, and M. M. A. Salama. "Optimal photovoltaic array reconfiguration to reduce partial shading losses." IEEE Trans. Sustain. Energy 4.1 (2013): 145-153.
\bibitem{b12} Storey, Jonathan P., Peter R. Wilson, and Darren Bagnall. "Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.
